### 2022-08-25 manuscript.Rmd
Adjust placement of Supplementary Figure S1

```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informeed",
  condition_minus = "Exclude_informed"
)
```

@@

```{r, figclusters, include=TRUE, fig.height=8}
# Plot thresholded cluster images
clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  theme(legend.position = "top")
```

>>>>

@@

```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", eval=TRUE}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informeed",
  condition_minus = "Exclude_informed"
)
```

```{r, figclusters, fig.height=8, include=FALSE}
# Plot thresholded cluster images
clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  theme(legend.position = "top")
```
